---
title: "testBernoulliKernel"
author: "Shakkya Ranasinghe"
date: "2023-09-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
here::i_am("Code/testBernoulliKernel.Rmd")
GInv <- MASS::ginv
f <- glue::glue
```

# Will attach more descriptive note late

Note contains 
  + Penalized likelihood method and its relation to this code 
  + Whats a reproducing kernel 
  + Bernoulli Reproducing Kernel (what is a Bernoulli polynomial and kernel) 
  + Matrix Algebra computation

# X and function values 
```{r model}
n = 100
x <- seq(1, pi, length.out = n)
y <- sin(x*6) # + rnorm(100, 0, 0.2)
plot(x, y)
```



# Bernoulli Reproducing Kernel

We need the Bernoulli polynomials to create the Kernel. In the kernel we will take m=2, so we'll need to build kernel for 0, 1, 2, 3, 4 (B~2m~)

```{r berPolynomial}
m = 2
v = m*2 # why did we define this?

b0 <- function(x) {
  return(rep(1, n))
}
b1 <- function(x) {
  return(x - 1/2)
}
b2 <- function(x) {
  return(x^2 - x + 1/6)
}
b3 <- function(x) {
  return(x^3 - 3/2*x^2 + 1/2*x)
}
b4 <- function(x) {
  return(x^4 - 2*x^3 + x^2 - 1/30)
}
```

Build the Kernel

```{r kernel}
require(rlang)
require(magrittr, quietly = TRUE) # masking set_names from rlang

bernoulliKernel <- function(x, y, m = 2) {
  # Check
  if (length(x) != length(y)) {
    stop("x and y should be of same length")
  }
  rKernel = 1
  for (v in 1:m) { # or is it m-1
    textToEval <- paste0("b", v) # create the function name
    f("Making Evaluation call {textToEval}") %>% print()
    rKernel = rKernel + 
      ((textToEval %>%
        call2(., x = x) %>% eval()) + # call2 creates a function, eval evaluates
        (textToEval %>%
           call2(., x = y) %>% eval())) / (factorial(v) ^ 2)
  }
  m = 2
  lastCall = paste0("b", 2*m) %>% call2(., x=abs(x-y)) 
  rKernel = rKernel + ((-1) ^ (m - 1)) * ((lastCall %>% eval()) / (factorial(2 * m)))
  return(rKernel)
}

kernel = bernoulliKernel(x, y, m = 3)
```


Fitting the values with `Bernoulli Kernel`

```{r fHat}
lambda = 1/(10**2)
I = diag(n)
# Coefficient
coef <- (kernel + n*lambda*I) %>% GInv()
coef <- coef %*% matrix(y)

# phi (not sure about this)
phi <- kernel %>% matrix()

# fitted values according to our model
fHat = (phi) * coef
fHat %>% c() -> fHat
```

Check fit with different `lambda` values and `n`

```{r}
require(dplyr)
require(ggplot2)

dfOri <- tibble(x, y)
dfFit <- tibble(x, fHat)
dfOri %>% 
  left_join(dfFit, by = 'x') %>% reshape2::melt(id = 'x') %>% 
  ggplot() + 
  geom_point(aes(x=x, y =value, col = variable))
  
  
```
```{r}
print("this")
```

