---
title: "testBernoulliKernel"
author: "Shakkya Ranasinghe"
date: "2023-09-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
here::i_am("Code/testBernoulliKernel.Rmd")
source(here::here("Code/utils.R"))

require(rlang)
require(magrittr, quietly = TRUE) # masking set_names from rlang

```

# Will attach more descriptive note late

Note contains 
  + Penalized likelihood method and its relation to this code 
  + Whats a reproducing kernel 
  + Bernoulli Reproducing Kernel (what is a Bernoulli polynomial and kernel) 
  + Matrix Algebra computation

# X and function values 
```{r model}
n = 100
x <- runif(n, 0, 1) # Assume these are our observations
y <- sin(x*12) + rnorm(100, 0, 0.2)  # Assume these are our observations
plot(x, y)
```



# Bernoulli Reproducing Kernel

We need the Bernoulli polynomials to create the Kernel. In the kernel we will take m=2, so we'll need to build kernel for 0, 1, 2, 3, 4 (B~2m~)

```{r berPolynomial}
m = 2

b0 <- b0 # From utils
b1 <- b1
b2 <- b2
b3 <- b3
b4 <- b4
```

Build the Kernel. Refer to [textbook pg 10](https://arxiv.org/pdf/2308.13905.pdf)

```{r kernel}
bernoulliKernel <- bernoulliKernel # from utils

kernel = bernoulliKernel(x, x, m = m)
```


Fitting the values with `Bernoulli Kernel`

```{r fHat}
lambda = 1/(10**5) # higher lambda (lower power) makes a naive fit. Optimal is around 5. Even lower lambda would make a jagged fit (exact fit to each observation)
I = diag(1, nrow = 100)
R = outer(x, x, FUN = bernoulliKernel, m = m)
# we're passing m as an argument to bernoulliKernel function
# we're taking the outer product of 

# Coefficient
coef <- (R + n*lambda*I) %>% GInv()
coef <- coef %*% matrix(y)

# phi (not sure about this)
phi <- R

# fitted values according to our model
fHat = t(phi) %*% coef
fHat %>% c() -> fHat
```

Plot to see the goodness of fit.

```{r}
require(dplyr)
require(ggplot2)

dfOri <- tibble(x, y)
dfFit <- tibble(x, fHat)
dfOri %>% 
  left_join(dfFit, by='x') %>%  # get the corresponding fitted value to x
  reshape2::melt(id='x') %>% # flatten the table so that we can plot as one variable but two groups
  ggplot() + 
  geom_point(aes(x=x, y=value, col=variable))

```
```{r}
print("this")
```

